# Findings - Words and Punctuation
## Word Count

```{r}
books_words <- books_words %>% arrange(desc(X2))
fanfic_words <- fanfic_words %>% arrange(desc(X_2))

#Gets a list of words that appear only in books or only in fanfiction
book.temp<-books_words %>% mutate(book_prop=X2/sum(books_words$X2,na.rm=TRUE))
fanfic.temp<-fanfic_words %>% mutate(fanfic_prop=X_2/sum(fanfic_words$X_2,na.rm=TRUE))

book.shared<-subset(book.temp,X1 %in% fanfic_words$X_1)
fanfic.shared<-subset(fanfic.temp,X_1 %in% books_words$X1)


book.shared$fanfic_prop <- fanfic.shared$fanfic_prop[match(book.shared$X1,fanfic.shared$X_1)]
lit.shared<-book.shared

#Higher dif = More Popular in Books
lit.shared$dif<-lit.shared$book_prop-lit.shared$fanfic_prop
lit.shared<-lit.shared %>% arrange(desc(dif))
shared.length<-length(lit.shared$X1)

book.popular<-lit.shared$X1[1:10]
fanfic.popular<-lit.shared$X1[(shared.length-9):shared.length-1]

cbind(book.popular,fanfic.popular)

#Unique Words to each group
# `%!in%` <- Negate(`%in%`)
# subset(book.temp,X1 %!in% fanfic_words$X_1)
# subset(fanfic.temp,X_1 %!in% books_words$X1)


```


## Punctuation

```{r echo = FALSE}
p<-ggplot(data=POS_punct,aes(x=POS_punctuation , y=proportion,fill=lit_type))+
  geom_bar(stat = 'identity',position = 'dodge')+
  theme_minimal()+ scale_y_continuous(expand=expansion(mult=c(0,0.1)))+labs(x='part of speech',y='proportion')
p <- p + guides(fill=guide_legend(title="Literature Type"))
p
```
Above we can see the punctuation used

It's worth nothing that the method we used for tokenizing punctuation results in a lot of simplification: colons, semi-colons, and ellipses are all classified as ':'.  Exclamation marks and periods are considered the same.  Despite this, there's still a bit that can be gleaned from this graphic: classic literature has a higher proportion of commas and partial sentence breaks, which might point towards more compound sentences, and the hashtag only appears in our fanfiction sample.